---
title: "R BnB"
output: github_document

---

```{r}
library(OpenStreetMap)
library(leaflet)
library(rgdal)
library(dplyr)
library(purrr)
library(htmlwidgets)
library(RColorBrewer)
library(classInt)
library(plotrix)  
library(ggmap)
library(magick)
library(ggthemes)
library(scales)

library(lubridate)
```

```{r}
df_light<-read.csv('data/listings_light.csv',stringsAsFactors = FALSE)
df_light_2015<-read.csv('data/listings_oct_2015.csv')
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
```{r}

# pal <- colorQuantile(
#   palette = "Reds",
#   domain = df_light$number_of_reviews,reverse = FALSE)
# 
# m<-leaflet(data = df_light) %>% addTiles() %>%
#   addCircleMarkers(~longitude, ~latitude, popup = ~as.character(name), label = ~as.character(name),stroke = FALSE, fillOpacity = 0.8,color = ~pal(number_of_reviews),radius=2) 
# 
# m
```
## With OSM
```{r fig.width=12, fig.height=12}

df_wedding<-df_light %>% filter(grepl('Mitte',neighbourhood_group))
range_lat<-range(df_wedding$latitude)
range_lon<-range(df_wedding$longitude)

# # téléchargement de la carte
# mapBerlin <- openmap(upperLeft = c(range_lat[1], range_lon[1]), 
#                   lowerRight = c(range_lat[2], range_lon[2]), 
#                   type = "stamen-toner")
# # affichage de la carte


# df_wedding <- cbind(df_wedding,projectMercator(df_wedding$latitude,df_wedding$longitude))

```

```{r fig.width=12, fig.height=12}
ggmap_berlin<- get_map(location = c(left = range_lon[1], bottom = range_lat[1], right =
  range_lon[2], top = range_lat[2]),source="google",color="bw")





```

```{r fig.width=12, fig.height=12}
plot_map<- function(df,title){
  title <-strsplit(title,'.csv')[[1]]
  col_neighbour<- grep('neigh',colnames(df),value = TRUE)
  
  df_mitte<-df %>% filter(grepl('Mitte',neighbourhood_group))
  color_hex_max='#ff5a5f'
  color_hex_min ='#0dc24b'
  col <- findColours(classIntervals(
            df_mitte$price, 5, style="quantile"),
            smoothColors(color_hex_min,3,color_hex_max)) 
  
  
  ggmap(ggmap_berlin)+ geom_point(aes(x=longitude, y=latitude), data=df_mitte, col=color_hex_max)+ggtitle(title)+theme(plot.title = element_text(size = 40, face = "bold"))+  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

  ggsave(filename = paste0("./data/maps/",title,".png"),
             width = 8,height=8,dpi = 150)

}
```

```{r}
filos<- list.files(path = "data/listings/")

print(filos)
```

```{r}
for (filo in filos){
  file_path = paste0("data/listings/",filo)
  
  df<-read.csv(file_path, stringsAsFactors = FALSE)
  plot_map(df,filo)
}
```



```{r}
list.files(path = "./data/maps/single_anim/", pattern = "*.png", full.names = T) %>% 
  map(image_read) %>% # reads each path file
  image_join() %>% # joins image
  image_animate(fps=1) %>% # animates, can opt for number of loops
  image_write("ndwi_aug_hgm.gif") # write to current dir
```
# Get summary bet neighbourhood
```{r}

df_neighbourhood <- data.frame()

for (filo in filos){
  file_path = paste0("data/listings/",filo)
  
  df<-read.csv(file_path, stringsAsFactors = FALSE)
  df<- df %>% filter(room_type=='Entire home/apt')
  groupy<-df %>% group_by(neighbourhood_group) %>% summarise(total_offers = n(), mean_price=mean(price))
  year_month<-strsplit(filo,'.csv')[[1]]
  
  groupy$year<-as.integer(strsplit(year_month,'_')[[1]][1])
  groupy$month<-as.integer(strsplit(year_month,'_')[[1]][2])
 
  
  df_neighbourhood<-rbind(df_neighbourhood,groupy)

}
df_neighbourhood<- df_neighbourhood %>% ungroup()
df_neighbourhood$date <- with(df_neighbourhood, ymd(sprintf('%04d%02d%02d', year, month, 1)))
#df_neighbourhood <- df_neighbourhood %>% filter(neighbourhood_group %in% c())
```

## filter on biggest areas
```{r}
 top_6 <- c("Charlottenburg-Wilm.","Friedrichshain-Kreuzberg","Mitte","Neukölln","Pankow","Tempelhof - Schöneberg")
mitte.areas<- c("Alexanderplatz","Brunnenstr. Nord","Brunnenstr. Süd","Moabit Ost","Moabit West","Osloer Straße" , "Parkviertel",       "Regierungsviertel","Tiergarten Süd","Wedding Zentrum")
df_neighbourhood <- df_neighbourhood %>% filter(neighbourhood_group %in% top_6)

```
# Plot evolution
```{r}
palette<-c("#075272","#ca3016","#ffba00","#23907b", "#897a8d","#70ddca")

ggplot(data=df_neighbourhood ,aes(x=date,y=total_offers,colour=neighbourhood_group))+theme_fivethirtyeight()+ geom_line(,size=1)+labs(colour="")+ theme(axis.title = element_text(),axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1),legend.text=element_text(size=10),plot.caption=element_text(size=8))+scale_x_date(breaks = pretty_breaks(15))+scale_colour_manual(values = palette)+ ggtitle("Berlin : Full appartments")+labs(caption = "©Clément Lefèvre 2017 (Sources : insideairbnb.com)")+ylab("online offers")


ggplot(data=df_neighbourhood ,aes(x=date,y=mean_price,colour=neighbourhood_group))+theme_fivethirtyeight()+ geom_line(,size=1)+labs(colour="")+ theme(axis.title = element_text(), axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1),legend.text=element_text(size=10),plot.caption=element_text(size=8))+scale_x_date(breaks = pretty_breaks(15))+scale_colour_manual(values = palette)+ ggtitle("Berlin : Full appartments")+labs(caption = "©Clément Lefèvre 2017 (Sources : insideairbnb.com)")+ylab("euros/night")
```
```{r}
df.may2017<-read.csv('data/listings/2017_05.csv')

df.mitte.2017 <- df.may2017 %>% filter(neighbourhood_group=='Mitte')
groupy.mitte.may.2017<- df.mitte.2017 %>% ungroup() %>% group_by(neighbourhood) %>% summarise(total= n())
groupy.mitte.may.2017  %>% select(neighbourhood) %>% collect %>% .[["neighbourhood"]]



```


# get summary per Mitte areas :
```{r}
df_neighbourhood.mitte <- data.frame()

for (filo in filos){
  file_path = paste0("data/listings/",filo)
  
  df<-read.csv(file_path, stringsAsFactors = FALSE)
  df<- df %>% filter(room_type=='Entire home/apt') %>% filter(neighbourhood %in% mitte.areas)
  groupy<-df %>% group_by(neighbourhood) %>% summarise(total_offers = n(), mean_price=mean(price))
  year_month<-strsplit(filo,'.csv')[[1]]
  
  groupy$year<-as.integer(strsplit(year_month,'_')[[1]][1])
  groupy$month<-as.integer(strsplit(year_month,'_')[[1]][2])
 
  
  df_neighbourhood.mitte<-rbind(df_neighbourhood.mitte,groupy)

}
df_neighbourhood.mitte<- df_neighbourhood.mitte %>% ungroup()
df_neighbourhood.mitte$date <- with(df_neighbourhood.mitte, ymd(sprintf('%04d%02d%02d', year, month, 1)))
```
# remove some areas :

```{r}
df_neighbourhood.mitte.light<- df_neighbourhood.mitte %>% filter(!grepl("Moabit|Tier|Park",neighbourhood))
```


# Plot evolution
```{r}
ggplot(data=df_neighbourhood.mitte.light ,aes(x=date,y=total_offers,colour=neighbourhood))+theme_fivethirtyeight()+ geom_line(,size=1)+labs(colour="")+ theme(axis.title = element_text(),axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1),legend.text=element_text(size=10),plot.caption=element_text(size=8))+scale_x_date(breaks = pretty_breaks(15))+ ggtitle("Mitte : Full appartments")+labs(caption = "©Clément Lefèvre 2017 (Sources : insideairbnb.com)")+ylab("online offers")+scale_colour_manual(values = palette)

ggplot(data=df_neighbourhood.mitte.light ,aes(x=date,y=mean_price,colour=neighbourhood))+theme_fivethirtyeight()+ geom_line(,size=1)+labs(colour="")+ theme(axis.title = element_text(),axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1),legend.text=element_text(size=10),plot.caption=element_text(size=8))+scale_x_date(breaks = pretty_breaks(15))+ ggtitle("Mitte: Full appartments")+labs(caption = "©Clément Lefèvre 2017 (Sources : insideairbnb.com)")+ylab("euros/night")+scale_colour_manual(values = palette)


```

ggplot(data=df_neighbourhood.mitte ,aes(x=date,y=mean_price,colour=neighbourhood))+theme_fivethirtyeight()+ geom_line(,size=1)+labs(colour="")+ theme(axis.title = element_text(), axis.title.x=element_blank(), axis.text.x = element_text(angle = 90, hjust = 1),legend.text=element_text(size=10),plot.caption=element_text(size=8))+scale_x_date(breaks = pretty_breaks(15))+scale_colour_manual(values = palette)+ ggtitle("AirBnb : Full appartments (mean price)")+labs(caption = "©Clément Lefèvre 2017 (Sources : insideairbnb.com)")+ylab("euros/night")
```
